---
title: "HW 01 - Halloween Candy"
author: "Yue Jiang"
date: "Add the date here. Due Wed, Jan 29 at 11:59p"
output:
  html_document: default
  pdf_document: default
---
```{r}
library(usethis)
use_git_config(user.name = "serenalimstrutt", user.email = "sl487@duke.edu")
```

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(fivethirtyeight)
```

# Exercise 1

```{r, ex-1-dataset-basics}
?candy_rankings
```

There are 85 observations and 13 variables. 


# Exercise 2

Categorical variables;
competitorname - the name of the Halloween Candy.
chocolate - does it contain chocolate?

Numerical Variables:
sugarpercent - the percentile of sugar it falls under within the dataset.
pricepercent - the unit price percentile compared to the rest of the set.

# Exercise 3

```{r, ex-3-winpercent-vs-chocolate}
ggplot(data = candy_rankings, mapping = aes(x = chocolate, y = winpercent)) +
  geom_point() +
  labs(title = "Win percentage of candy generally increases with chocolate")

```

We can see that there is an association between a the candy containing chocolate and having a higher win percentage.

# Exercise 4
```{r}
candy_rankings %>%
  filter(winpercent < "32.26") %>%
  arrange(desc(winpercent)) %>%
  mutate(win_percent = round(winpercent, digits = 2)) %>%
  select(competitorname, win_percent) 
```

# Exercise 5
```{r}
candy_rankings %>%
  summarise(mean_winpercent = mean(winpercent))

candy_rankings <- candy_rankings %>%
  mutate(chocolate_1 = ifelse(chocolate == TRUE, "choc", "no choc"))

candy_rankings %>%
  filter(chocolate_1 == "choc")
```

# Exercise 6
```{r}
candy_rankings %>%
  filter(fruity == TRUE) %>%
  select(competitorname, winpercent) %>%
  arrange(desc(winpercent)) %>%
  slice(1:3)
```


# Exercise 7

# Exercise 8

Don't forget to knit to .pdf and upload on Gradescope! You must associate each question with a page and the "Overall section" with the first page.
